\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-07-30 popl-2019-journal-v/paper.tex
[POPLjv] Update todos

\begin{jversion}
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds X and Y and Z.
  \todo{new version of TR?}
  This paper is accompanied by a technical report~\citep{technical_report_popl} with the elided details and proof.
\end{jversion}

@@

\dominique{Relate full-abstraction to other notions of secure compilation}

\dominique{Relate to Stelios' CSF 2019 paper}

\dominique{Relate to Thomas Van Strydonck's ICFP19 paper which uses linear capabilities (at a higher level) to enforce separation logic in a fully abstract way.}

>>>>

\begin{jversion}
  % TODO add outline of new work
  This text is an extended version of a paper that was presented at POPL 2019~\citep{skorstengaard_stktokens_2019}.
  Compared to the earlier text, this version adds X and Y and Z.
  This paper is accompanied by a technical report~\citep{technical_report_popl} with the elided details and proof.
\end{jversion}

@@

\dominique{TODO Relate full-abstraction to other notions of secure compilation}

\dominique{TODO Relate to Stelios' CSF 2019 paper}

\dominique{TODO Relate to Thomas Van Strydonck's ICFP19 paper which uses linear capabilities (at a higher level) to enforce separation logic in a fully abstract way.}
